---
title: "Homework 2"
author: "Adrien, Natalia, Laura"
date: "7/2/2019"
output: html_document

---

The objectives of this homework assignment are the following:

* Learn how program effectively using if/else and iterations statements;
* Become familiar with using data frame objects and mapping packages;
* Constructing a portfolio;
* Become familiar with GitHub and using it as a collaborative tool.

This project must be done using GitHub and respect the following requirements:

1. Each member of the group must commit at least once.
2. All commit messages must be reasonably clear and meaningful.
3. Your GitHub repository must include at least one issue containing some form of a TO DO list.

#Problem 1: Fizz Buzz

Write a program that prints the numbers from 1 to 1000. But for multiples of three print “Fizz” instead of the number and for the multiples of five print “Buzz”. For numbers which are multiples of both three and five print “FizzBuzz”.
```{r}
a =1:1000
number=0
for (i in 1:length(a)) {
  if (a[i]%%3==0 & a[i]%%5==0){
    print(paste(a[i],"FizzBuzz"))
  }else if(a[i]%%3==0){
    print(paste(a[i],"Fizz"))
  }else if(a[i]%%5==0){
    print(paste(a[i],"Buzz"))
  }else{
    print(paste(a[i],"is not divisable by neither 3 nor 5"))
  }
}
  

```


# Problem 2 Random Walk

```{r}
# number of steps 

steps <- 10^4
set.seed(1982)
Ut <- runif(steps)

# the probability to chose any 6 direction
probs <- c(0.1666667,0.3333334,0.5000001,0.6666668,0.8333335)


step_direction <- matrix(0, steps+1, 3) # 3* possible directions

for(i in seq(2,steps+1)){
  # draw a random number from a uniform distribution
  rn = Ut[i-1]
  
  # go right if the rn is less than 0.14
  if(rn < probs[1]){step_direction[i,1] = 1}
  
  # go left if the rn is between 0.14 & 0.28
  if(rn >= probs[1] & rn < probs[2]) {step_direction[i,1] = -1}
  
  # go forward if the rn is between 0.28 & 0.42
  if(rn >= probs[2] & rn < probs[3]) {step_direction[i,2] = 1}
  
   # go backward if the rn is between 0.42 & 0.57
  if(rn >= probs[3] & rn < probs[4]) {step_direction[i,2] = -1}
  
   # go up if the rn is between 0.57 & 0.71
  if(rn >= probs[4] & rn < probs[5]) {step_direction[i,3] = 1}
   # go down if the rn is above 85
  
  if(rn > probs[5]) {step_direction[i,3] = -1}
  
}
step_direction[,1]


# Cumulative steps
position = data.frame(x = cumsum(step_direction[, 1]), 
                      y = cumsum(step_direction[, 2]),
                      z = cumsum(step_direction[, 3]))
position[10001,]


```


# Problem 3  maps 


```{r}

# Make Map using google API Key 

teams = c("Real Madrid", "FC Barcelona","Atlético Madrid","Athletic Bilbao","Valencia")
champions = c(33,25,10,8,6)
city = c("Madrid","Barcelona","Madrid","Bilbao","Valencia")

data <- data.frame(teams,champions,city)
str(data)

# Make map with google project and API keys: 
library(ggmap)
#register_google(key = "", write=TRUE)
lat_long = geocode(city)
lat_long


# Make Map Manually 


lat_long[1,] <- c(-3.703630,40.414618) # Madrid 

lat_long[2,] <- c( 2.177950,41.391378) # Barcelona
lat_long[3,] <- c(-3.703630,40.414618) # Madrid
lat_long[4,] <- c( -2.932364, 43.261062) # Bilbao
lat_long[5,] <- c( -0.366909,39.456967) # Valencia

lat_long
 (map <- get_map(c(left=-12.5, bottom = 35, right=5.5, top=45)))
p = ggmap(map,extent = "device")
p + geom_point(data = lat_long, aes(x=lon, y=lat, size=champions, col=teams), alpha = 1)
```


# Problem 



















